---
title: "CHOP Coagulation Method Comparison & Bias Estimation"
date: '`r Sys.Date()`'
output: 
  pdf_document:
    latex_engine: pdflatex
    includes:
      in_header: header.tex
header-includes:
  - \usepackage[table]{xcolor}
  - \usepackage{float}  # Include the float package
  - \definecolor{passGreen}{RGB}{34, 139, 34}
  - \definecolor{failRed}{RGB}{205, 92, 92}
params:
  tabledata: "currentData"
  data: "final_data"
  m1: "old"
  m2: "new"
  syx: 1
  regmodel: "LinReg"
  cimethod: "analytical"
  metbootci: 'BCa'
  batype: 3
  ciarea: TRUE
  legend: TRUE
  identity: TRUE
  addcor: TRUE
  cormet: 'pearson'
  name: ''
  test: ''
  reagentLot: ''
  expiration: ''
  date: ''
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results='asis')
```

### Test Information

```{r}
library(knitr)
library(kableExtra)

# Assuming params contains test, reagentLot, expiration, date
df_test_long <- data.frame(
  Parameter = c("Test", "Reagent Lot", "Expiration", "Date"),
  Value = c(params$test, params$reagentLot, params$expiration, params$date)
)

# For HTML output
if(knitr::is_html_output()) {
  kable(df_test_long, "html", align = 'c') %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                  full_width = F, position = "center")
}

# For PDF output
if(knitr::is_latex_output()) {
  kable(df_test_long, "latex", booktabs = TRUE, align = 'c') %>%
    kable_styling(latex_options = c("striped", "HOLD_position"))
  
}
```



```{r dataframe, comment = '', echo=FALSE, warning = FALSE, message = FALSE,  results='asis'}
library(mcr)
library(pander)
df <- params$tabledata

if(knitr::is_html_output()) {
      tableHTML <- generateKableTable(df, "html")
     cat(tableHTML)# <- generateKableTable(df, "html")
}

if(knitr::is_latex_output()) {
  tablePDF <- generateKableTable(df, "latex")
  tablePDF%>%
    kable_styling(latex_options = c("HOLD_position"))
}

  

```


```{r regression plot, echo = FALSE, results = 'markup', fig.show = 'asis', message = FALSE}
library(mcr)
a <- params$data
if (is.null(a)) {
return(NULL)} else {
names(a) <- c('Sample','M1', 'M2')
data1<- mcreg(a$M1, a$M2, error.ratio = params$syx, 
method.reg = params$regmodel, method.ci = params$cimethod,
method.bootstrap.ci = params$metbootci, slope.measure = "radian", na.rm = TRUE)
MCResult.plot(data1, ci.area = params$ciarea, 
add.legend = params$legend, identity = params$identity,
add.cor = params$addcor, x.lab = params$m1,
y.lab = params$m2, cor.method = params$cormet, 
equal.axis = TRUE, add.grid = TRUE)
}
```


```{r statistics, echo = FALSE, comment = '', warning = FALSE, message = FALSE}
library(mcr)
library(pander)
a <- params$data
if (is.null(a)) {
return(NULL)} else {
names(a) <- c('Sample','M1', 'M2')
data1 <- mcreg(a$M1, a$M2, error.ratio = params$syx, 
method.reg = params$regmodel, method.ci = params$cimethod,
method.bootstrap.ci = params$metbootci, slope.measure = "radian",
mref.name = params$m1, mtest.name = params$m2, na.rm = TRUE)
pander(getCoefficients(data1), caption = "Estimate (EST), standard error (SE) and upper-lower confidence interval (UCI-LCI) for intercept and slope", style = "grid")
}
```


```{r coef plot, echo = FALSE, comment = '', warning = FALSE, message = FALSE}
library(mcr)
a <- params$data
if (is.null(a)) {
return(NULL)} else {
names(a) <- c('Sample','M1', 'M2')
data1 <- mcreg(a$M1, a$M2, error.ratio = params$syx, 
method.reg = params$regmodel, method.ci = params$cimethod,
method.bootstrap.ci = params$metbootci, slope.measure = "radian",
mref.name = params$m1, mtest.name = params$m2, na.rm = TRUE)
compareFit(data1)
}
```


```{r BA plot, echo=FALSE, results = 'markup'}
library(mcr)
a <- params$data
if (is.null(a)) {
return(NULL)} else {
names(a) <- c('Sample','M1', 'M2')
data1 <- mcreg(a$M1, a$M2,
mref.name = params$m1, mtest.name = params$m2, na.rm = TRUE)
MCResult.plotDifference(data1, plot.type = params$batype, add.grid = TRUE)
MCResult.plotDifference(data1, plot.type = 4, add.grid = TRUE) # Hard code want percent BA
}
```


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```


#### Data is processed using R language^1^, shiny web application framework^2^ and mcr package^3^. Shinydashboard^4^, rhandsontable^5^ and pander^6^ are used for website construction. Rmarkdown^7^ is used for converting results into PDF and HTML files.

##### References and packages:

1. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. Version: `r getRversion()` URL: https://www.R-project.org
2. shiny: Web Application Framework for R. Version `r packageDescription("shiny")$Version` URL: http://CRAN.R-project.org/package=shiny
3. mcr: Method Comparison Regression. Version: `r packageDescription("mcr")$Version` URL: http://CRAN.R-project.org/package=mcr
4. shinydashboard: Create Dashboards with 'Shiny'. Version: `r packageDescription("shinydashboard")$Version` URL: http://rstudio.github.io/shinydashboard
5. rhandsontable: Interface to the 'Handsontable.js' Library. Version: `r packageDescription("rhandsontable")$Version` URL: http://jrowen.github.io/rhandsontable
6. pander: An R Pandoc Writer. Version: `r packageDescription("pander")$Version` URL: http://rapporter.github.io/pander
7. rmarkdown: Dynamic Documents for R. Version: `r packageDescription("rmarkdown")$Version` URL: http://rmarkdown.rstudio.com
